paper

### 2022-03-31 outputs/paper.Rmd
commit to update my file

```{r}
# region

child <- region %>% 
  select(-c(character, total)) %>% 
  pivot_longer(!background, names_to = "x", values_to = "percentage")

>>>>

```{r, echo = FALSE}
# make dataset into long format
# recode names
child <- region %>% 
  select(-c(character, total)) %>% 
  pivot_longer(!background, names_to = "x", values_to = "percentage") %>% 
  mutate(x = recode(x,
                    'caretaker_respondent' = 'respondent',
                    'caretaker_partner' = 'partner',
                    'caretaker_other_relative' = 'other relative',
                    'caretaker_other_male_child' = 'other male child',
                    'caretaker_other_female_child' = 'other female child',
                    'caretaker_other' = 'other',
                    'caretaker_not_worked_since_birth' = 'not worked since birth',
                    'caretaker_neighbor' = 'neighbour',
                    'caretaker_missing' = 'missing',
                    'caretaker_hired' = 'hired',
                    'caretaker_child_in_school' = 'child in school',
                    'no_child_under_six' = 'no child under six',
                    'one_more_child_under_six' = 'one or more child under six',
                    'number_of_employed_women' = 'number of employed women'))

# plot bar graph for caretaker comparisons and administrative regions
child %>% 
  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity') + 
  labs(x = "caretaker",
       y = "percentage of XXX",
       fill = "Administrative regions") +
  theme_minimal() +
  coord_flip() +
  facet_wrap(~background) +
  theme(legend.position = "bottom")

```{r, echo = FALSE}
# number of employed women selected in the admiistrative regions
child %>% 
  filter(x == "number of employed women") %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity',
           position = 'dodge') +
  labs(x = 'Administrative regions',
       y = 'Number of employed women') +
  theme_minimal() +
  scale_fill_brewer(palette = 'Set3') +
  theme(legend.position = "bottom")
```

```{r, echo = FALSE}
# looking at the number of employed women selected in the different administrative regions
# with the child under six
child %>% 
  filter(x == "no child under six" | x == "one or more child under six") %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity') +
  labs(x = "child",
       y = "percentage of XXX",
       fill = "Administrative regions") +
  theme_minimal() +
  coord_flip() +
  facet_wrap(~background)
